---
title: "Homework 6 solutions"
author: "Yanhao Li"
output: github_document
---

```{r set_up, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)


scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

```{r load libraries}
library(modelr)
library(mgcv)
library(p8105.datasets)
```


### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ","),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest" ~ 0,
      disposition == "Closed by arrest" ~ 1
    )
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa,AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore,MD")

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Problem 2

Load and clean the data for regression analysis

```{r load+clean}
bw_df = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  drop_na() %>% 
  mutate(
    babysex = case_when(
      babysex == 1 ~ "male",
      babysex == 2 ~ "female"
    ),
    frace = case_when(
      frace == 1 ~ "white",
      frace == 2 ~ "black",
      frace == 3 ~ "asian",
      frace == 4 ~ "puerto rican",
      frace == 8 ~ "other",
      frace == 9 ~ "unknown"
    ),
    malform = case_when(
      malform == 0 ~ "absent",
      malform == 1 ~ "present"
    ),
    mrace = case_when(
      mrace == 1 ~ "white",
      mrace == 2 ~ "black",
      mrace == 3 ~ "asian",
      mrace == 4 ~ "puerto Rican",
      mrace == 8 ~ "other"
    ),
    babysex = factor(babysex),
    frace = factor(frace),
    malform = factor(malform),
    mrace = factor(mrace)
    )
```

Propose a regression model for birthweight

My hypothesized structure includes `babysex`, `bhead`, `blength`, `gaweeks`, `smoken`, and `wtgain`. P-values of all factors mentioned before are lower than 0.05. Consequently, I keep all factors. 

```{r propose}
fit = lm(bwt ~ babysex + bhead + blength + gaweeks + smoken + wtgain, data = bw_df)

broom::glance(fit)

broom::tidy(fit) %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable(digits = 3)
```

Show a plot of model residuals against fitted values

```{r residual+fitted}
bw_df %>% 
  add_residuals(fit) %>%
  add_predictions(fit) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = .2) +
  labs(
    x = "fitted values",
    y = "model residuals",
    title = "model residuals against fitted values"
  )
```

Compare your model to two others

```{r}

```



## Problem 3