---
title: "Homework 6 solutions"
author: "Yanhao Li"
output: github_document
---

```{r set_up, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)


scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

```{r load libraries}
library(modelr)
library(mgcv)
library(p8105.datasets)
```


### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ","),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest" ~ 0,
      disposition == "Closed by arrest" ~ 1
    )
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa,AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore,MD")

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Problem 2

Load and clean the data for regression analysis

```{r load+clean}
bw_df = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  drop_na() %>% 
  mutate(
    babysex = case_when(
      babysex == 1 ~ "male",
      babysex == 2 ~ "female"
    ),
    frace = case_when(
      frace == 1 ~ "white",
      frace == 2 ~ "black",
      frace == 3 ~ "asian",
      frace == 4 ~ "puerto rican",
      frace == 8 ~ "other",
      frace == 9 ~ "unknown"
    ),
    malform = case_when(
      malform == 0 ~ "absent",
      malform == 1 ~ "present"
    ),
    mrace = case_when(
      mrace == 1 ~ "white",
      mrace == 2 ~ "black",
      mrace == 3 ~ "asian",
      mrace == 4 ~ "puerto Rican",
      mrace == 8 ~ "other"
    ),
    babysex = factor(babysex),
    frace = factor(frace),
    malform = factor(malform),
    mrace = factor(mrace)
    )
```

Propose a regression model for birthweight

My hypothesized structure includes `babysex`, `bhead`, `blength`, `gaweeks`, `smoken`, and `wtgain`. P-values of all factors mentioned before are lower than 0.05. Consequently, I keep all factors. 

```{r propose}
fit = lm(bwt ~ babysex + bhead + blength + gaweeks + smoken + wtgain, data = bw_df)

broom::glance(fit)

broom::tidy(fit) %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable(digits = 3)
```

Show a plot of model residuals against fitted values

Generally, points are evenly distributed above and below the x-axis. However, there are some outliers at top left corner. 

```{r residual+fitted}
bw_df %>% 
  add_residuals(fit) %>%
  add_predictions(fit) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = .2) +
  labs(
    x = "fitted values",
    y = "model residuals",
    title = "model residuals against fitted values"
  )
```

Compare your model to two others

Violin plot shows that my model has the lowest RMSE.

```{r compare}
fit_lb_ga = lm(bwt ~ blength + gaweeks, data = bw_df)

fit_hc_l_s = lm(bwt ~ bhead * blength * babysex, data = bw_df)

broom::tidy(fit_lb_ga) %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable(digits = 3)

broom::tidy(fit_hc_l_s) %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable(digits = 3)

crossv_mc(bw_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) %>% 
  mutate(
    fit = map(.x = train, ~lm(bwt ~ babysex + bhead + blength + gaweeks + smoken + wtgain, data = .x)),
    fit_lb_ga = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    fit_hc_l_s = map(.x = train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_mine = map2_dbl(.x = fit, .y = test, ~rmse(model = .x, data = .y)),
    rmse_lb_ga = map2_dbl(.x = fit_lb_ga, .y = test, ~rmse(model = .x, data = .y)),
    rmse_hc_l_s = map2_dbl(.x = fit_hc_l_s, .y = test, ~rmse(model = .x, data = .y))
  ) %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin() +
  labs(
    title = "rmse against model"
  )
```

## Problem 3

Download data

```{r download}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Produce estimates of these two quantities

```{r estimate}
est = 
  weather_df %>% 
  bootstrap(5000, id = "strap_number") %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    tidy = map(models, broom::tidy),
    glance = map(models, broom::glance)
    ) %>% 
  select(strap_number, tidy, glance) %>% 
  unnest(tidy, glance) %>% 
  select(strap_number, term, estimate, r.squared)
```

Plot the distribution of your estimates

Two plots seem to show normal distribution. However, they are a little bit skewed in the left.

```{r plot}
est %>%
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(
    title = "distribution of r.squared"
  )

est %>%
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>% 
  janitor::clean_names() %>% 
  mutate(
    log = log(intercept*tmin)
  ) %>%
  ggplot(aes(x = log)) +
  geom_density() +
  labs(
    x = "log(beta0*beta1)",
    title = "distribution of log(beta0*beta1)"
  )
```

Provide a 95% confidence interval for r.squared and log(beta0*beta1)

```{r}

```

